Time spent for each member, and respective member's tasks:

\begin{figure}[h] % Kunde inte låta bli att pilla. Sorry! ;) /OP
  \centering
  \begin{tabular}{|l|l|c|}
    \hline
    Group Member & Main Tasks & Total Time \\
    \hline
    Niklas Blomqvist & Analysis code & $\sim$65\\
    Philip Johansson & Analysis code & $\sim$70\\
    Matteus Laurent & Vol/Bal code, project coordinating & $\sim$75\\
    Johan Levinsson	& Top TB code &	$\sim$55\\
    Oscar Petersson	& Keyboard code, documentation & $\sim$70\\
    Erik Peyronsson	& VGA code modifications & $\sim$70 \\
    \cline{3-3}
    && 405 h\\
    \hline
  \end{tabular}
\end{figure}

The overarching theme of the project execution would have to be the difficulties faced when one or more members' participation was prevented by illness or similar obstacles, ensuring a less than ideal attendance. Our project group was set back early on because of this very reason, leading to us trailing the schedule by approximately a week. However, the effort invested to catch up was admirable and sufficient, allowing for the eventual completion of the project. Aside from this, the project went mostly according to plan, with a few notable exceptions.

Cooperation and coordination within the group was satisfactory. The project manager was given sufficient authority to lead the distribution and coordination of tasks. A certain level of trust combined with good design of the module overview allowed for more individual workloads, without sacrificing shared communication and system understanding.

All things considered, the design specification was the task that exceeded its set aside time the most. This was due to the document outlining a lot more module details than originally planned, ultimately giving an indepth view of the system. The document was not only expanded upon on recommendation from our project supervisor, but also because of our own natural inquiry when discussing the design overview. Laying the groundwork this way gave voice to design uncertainties early on, and thus helped a lot with subsequent tasks.

Thanks to a thorough design specificiation, the foundation for our first prototype essentially wrote itself. The initial stages of coding were completed swiftly, making up for any time lost (and more) on writing the design document.
